Lessons learned from bugs in models of human history

### 2020-08-19 paper_compilable.tex
created compilable tex document for AJHG

\bibliographystyle{unsrtnat}
\bibliography{paper}

>>>>

\bibliographystyle{unsrtnat}
\begin{thebibliography}{18}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Kelleher et~al.(2016)Kelleher, Etheridge, and
  McVean]{kelleher2016efficient}
Jerome Kelleher, Alison~M Etheridge, and Gilean McVean.
\newblock Efficient coalescent simulation and genealogical analysis for large
  sample sizes.
\newblock \emph{PLoS computational biology}, 12\penalty0 (5):\penalty0
  e1004842, 2016.

\bibitem[Nelson et~al.(2020)Nelson, Kelleher, Ragsdale, Moreau, McVean, and
  Gravel]{nelson2020accounting}
Dominic Nelson, Jerome Kelleher, Aaron~P Ragsdale, Claudia Moreau, Gil McVean,
  and Simon Gravel.
\newblock Accounting for long-range correlations in genome-wide simulations of
  large cohorts.
\newblock \emph{PLoS genetics}, 16\penalty0 (5):\penalty0 e1008619, 2020.

\bibitem[Kelleher and Lohse(2020)]{kelleher2020coalescent}
Jerome Kelleher and Konrad Lohse.
\newblock Coalescent simulation with msprime.
\newblock In Julien~Y. Dutheil, editor, \emph{Statistical Population Genomics},
  pages 191--230. Springer US, New York, NY, 2020.

\bibitem[Hudson(2002)]{hudson2002generating}
Richard~R. Hudson.
\newblock Generating samples under a {Wright-Fisher} neutral model of genetic
  variation.
\newblock \emph{Bioinformatics}, 18\penalty0 (2):\penalty0 337--338, 2002.

\bibitem[Gutenkunst et~al.(2009)Gutenkunst, Hernandez, Williamson, and
  Bustamante]{gutenkunst2009inferring}
Ryan~N Gutenkunst, Ryan~D Hernandez, Scott~H Williamson, and Carlos~D
  Bustamante.
\newblock Inferring the joint demographic history of multiple populations from
  multidimensional snp frequency data.
\newblock \emph{PLoS genetics}, 5\penalty0 (10):\penalty0 e1000695, 2009.

\bibitem[Kelleher et~al.(2019)Kelleher, Wong, Wohns, Fadil, Albers, and
  McVean]{kelleher2019inferring}
Jerome Kelleher, Yan Wong, Anthony~W Wohns, Chaimaa Fadil, Patrick~K Albers,
  and Gil McVean.
\newblock Inferring whole-genome histories in large population datasets.
\newblock \emph{Nature genetics}, 51\penalty0 (9):\penalty0 1330--1338, 2019.

\bibitem[Albers and McVean(2020)]{albers2020dating}
Patrick~K Albers and Gil McVean.
\newblock Dating genomic variants and shared ancestry in population-scale
  sequencing data.
\newblock \emph{PLoS biology}, 18\penalty0 (1):\penalty0 e3000586, 2020.

\bibitem[Tong and Hernandez(2020)]{tong2020population}
Dominic~MH Tong and Ryan~D Hernandez.
\newblock Population genetic simulation study of power in association testing
  across genetic architectures and study designs.
\newblock \emph{Genetic epidemiology}, 44\penalty0 (1):\penalty0 90--103, 2020.

\bibitem[Zhou et~al.(2018)Zhou, Tian, Browning, and Browning]{zhou2018popdemog}
Ying Zhou, Xiaowen Tian, Brian~L Browning, and Sharon~R Browning.
\newblock {POPdemog}: visualizing population demographic history from
  simulation scripts.
\newblock \emph{Bioinformatics}, 34\penalty0 (16):\penalty0 2854--2855, 2018.

\bibitem[Pfaffelhuber et~al.(2020)Pfaffelhuber, Grundner-Culemann, Lipphardt,
  and Baumdicker]{pfaffelhuber2020choose}
Peter Pfaffelhuber, Franziska Grundner-Culemann, Veronika Lipphardt, and Franz
  Baumdicker.
\newblock How to choose sets of ancestry informative markers: A supervised
  feature selection approach.
\newblock \emph{Forensic Science International: Genetics}, 46:\penalty0 102259,
  2020.

\bibitem[Martin et~al.(2017)Martin, Gignoux, Walters, Wojcik, Neale, Gravel,
  Daly, Bustamante, and Kenny]{martin2017human}
Alicia~R Martin, Christopher~R Gignoux, Raymond~K Walters, Genevieve~L Wojcik,
  Benjamin~M Neale, Simon Gravel, Mark~J Daly, Carlos~D Bustamante, and
  Eimear~E Kenny.
\newblock Human demographic history impacts genetic risk prediction across
  diverse populations.
\newblock \emph{The American Journal of Human Genetics}, 100\penalty0
  (4):\penalty0 635--649, 2017.

\bibitem[Gravel et~al.(2011)Gravel, Henn, Gutenkunst, Indap, Marth, Clark, Yu,
  Gibbs, Bustamante, Project, et~al.]{gravel2011demographic}
Simon Gravel, Brenna~M Henn, Ryan~N Gutenkunst, Amit~R Indap, Gabor~T Marth,
  Andrew~G Clark, Fuli Yu, Richard~A Gibbs, Carlos~D Bustamante, 1000~Genomes
  Project, et~al.
\newblock Demographic history and rare allele sharing among human populations.
\newblock \emph{Proceedings of the National Academy of Sciences}, 108\penalty0
  (29):\penalty0 11983--11988, 2011.

\bibitem[Popejoy and Fullerton(2016)]{popejoy2016genomics}
Alice~B Popejoy and Stephanie~M Fullerton.
\newblock Genomics is failing on diversity.
\newblock \emph{Nature News}, 538\penalty0 (7624):\penalty0 161, 2016.

\bibitem[Adrion et~al.(2020)Adrion, Cole, Dukler, Galloway, Gladstein, Gower,
  Kyriazis, Ragsdale, Tsambos, Baumdicker, et~al.]{adrion2019community}
Jeffrey~R Adrion, Christopher~B Cole, Noah Dukler, Jared~G Galloway, Ariella~L
  Gladstein, Graham Gower, Christopher~C Kyriazis, Aaron~P Ragsdale, Georgia
  Tsambos, Franz Baumdicker, et~al.
\newblock A community-maintained standard library of population genetic models.
\newblock \emph{eLife}, 9:\penalty0 e54967, 2020.

\bibitem[Ralph et~al.(2020)Ralph, Thornton, and Kelleher]{ralph2020efficiently}
Peter Ralph, Kevin Thornton, and Jerome Kelleher.
\newblock Efficiently summarizing relationships in large samples: a general
  duality between statistics of genealogies and genomes.
\newblock \emph{Genetics}, 2020.

\bibitem[Jouganous et~al.(2017)Jouganous, Long, Ragsdale, and
  Gravel]{jouganous2017inferring}
Julien Jouganous, Will Long, Aaron~P Ragsdale, and Simon Gravel.
\newblock Inferring the joint demographic history of multiple populations:
  beyond the diffusion approximation.
\newblock \emph{Genetics}, 206\penalty0 (3):\penalty0 1549--1567, 2017.

\bibitem[Ragsdale and Gravel(2019)]{ragsdale2019models}
Aaron~P Ragsdale and Simon Gravel.
\newblock Models of archaic admixture and recent history from two-locus
  statistics.
\newblock \emph{PLoS genetics}, 15\penalty0 (6):\penalty0 e1008204, 2019.

\bibitem[Hagberg et~al.(2008)Hagberg, Swart, and S~Chult]{hagberg2008exploring}
Aric Hagberg, Pieter Swart, and Daniel S~Chult.
\newblock Exploring network structure, dynamics, and function using networkx.
\newblock Technical report, Los Alamos National Lab.(LANL), Los Alamos, NM
  (United States), 2008.

\end{thebibliography}
